Evaluating Russia's Response to the COVID-19 Pandemic: An Analysis of High Excess Death Rates Despite High GHS Index

### 2024-02-15 paper/paper.qmd
Minor edit to appendix plot.

```{r}
#| echo: false
#| eval: true
#| label: tbl-appendix
#| tbl-cap: "Cleaned Data showing Excess Death Rate and GHS index for a subset of countries"
#| tbl-cap-location: bottom
#| warning: false

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-appendix
#| tbl-cap: "Cleaned Data showing Excess Death Rate and GHS index for a subset of countries"
#| warning: false
